### 2017-10-01 TF-vldb2018/sec-dynamicTopk.tex

\subsection{Unified Incremental Framework}
%\label{subsec-framework}

@@

\stitle{(1) Localization with pattern fragmentation}. 
We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
(3) $E_{fi}$ is exactly the edges in $P$ on $V_{fi}$, and (4) $C=E_P \setminus (E_{f1}\cup\ldots\cup E_{fh})$.

@@

\vspace{-0.5ex}
\begin{theorem}
\label{thm-compose}
Let $\{P_{f1},\ldots,P_{fh}\}$ be an $h$-fragmentation of pattern $P$.
For any ball $\ball{}_i$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}_i$ for $P_{fi}$ via graph simulation,
and $M$ be the maximum match relation in $\ball{}_i$ for $P$ via graph simulation, respectively,
then $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
\end{theorem}

We also say that $M_i$ is a {\em partial match relation} in ball $\ball{}_i$ for $P$ via graph simulation.
%By Theorem~\ref{thm-compose}, instead of computing $M$ in $\ball{}$ \wrt\ $P$ directly, we can compute $M$ by first computing each $M_i$ in $\ball{}$ \wrt\ $P_{fi}$,
%and then combining them together.
By the nature of graph simulation~\cite{infsimu95}, $\bigcup_{i=1}^{h}M_{i}$ is actually an intermediate result of $M$.
%such that the method above does not incur additional computation cost.
Once we have the maximum match relation $M$ for $P$ in $\ball{}_i$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.

@@

%We already know that pattern updates $\Delta P$ on $P$ can be treated as the updates $\Delta P$ on $P_{fi}$ or $C$ of $P$.
%If we have cached the maximum match relations of all pattern fragments,
By storing $\tilde{M}(P,G)$, we have $\bigcup_{i=1}^{h}M_{i}$ for each ball $\ball{}$,
and we can simply update $M_i$ while leaving other parts untouched. That is, we indeed compute for $P_{fi}\oplus\Delta P(\ball{})$, instead of $P\oplus\Delta P(\ball{})$, and combine all $P_{fi}\oplus\Delta P(\ball{})$ derive $P\oplus\Delta P(\ball{})$.
Even better, the updates $\Delta P$ on $C$ of $P$ only involve with a simple combination process, avoiding the computation for any pattern fragments.

@@

\stitle{(2) Localization with affected balls (\affballsx)}.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computations.

@@

%\vspace{-0.5ex}
\stitle{(3) Algorithm framework}. We now provide a unified incremental algorithm to handle both pattern and data updates,
based on pattern fragmentation and affected balls.

@@

\etitle{(i) Identifying \affballsx}.
Algorithm \inc invokes two different procedures to identify \affballsx for separate $\Delta P$ or $\Delta G$, respectively.
For  simultaneous $\Delta P$ and $\Delta G$, \inc takes the union of the \affballsx produced by  the two procedures.

\etitle{(ii) Update partial match relations in \affballsx}.
For a ball affected by $\Delta P$, \inc updates the partial match relations for the updated pattern fragments with incremental computation;
For a ball affected by $\Delta G$, \inc updates the partial match relations for all pattern fragments;
And, for a ball affected by both $\Delta P$ and $\Delta G$, \inc follows the same way as $\Delta G$ only.
Meanwhile, auxiliary structure \fb (to be seen shortly) is updated for handling continuous separate and simultaneous pattern and data updates.

\etitle{(iii) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
	\begin{center}
		\subfigure{\label{fig-auxstr-index}
			\includegraphics[scale=0.585]{./fig/fig-auxstr-index.eps}}
		\subfigure{\label{fig-inc-maintain-unit}
			\quad\quad \vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-unit.eps}}
		\subfigure{\label{fig-inc-maintain-batch}
			\vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-batch.eps}}
		\vspace{-2ex}
		\caption{Example auxiliary data structures}
		\label{fig-auxiliary-structures}
		\vspace{-4ex}
	\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsection{A Unified Incremental Framework}
\label{subsec-framework}

@@

\stitle{(I) Localization with pattern fragmentation}.
We say that \{$P_{f1}(V_{f1}, E_{f1})$, $\ldots$, $P_{fh}(V_{fh}, E_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
(3) $E_{fi}$ is exactly the edges in $P$ on $V_{fi}$, and (4) $C=E_P \setminus (E_{f1}\cup\ldots\cup E_{fh})$.

@@

\vspace{-0.5ex}
\begin{theorem}
\label{thm-compose}
Let $\{P_{f1},\ldots,P_{fh}\}$ be an $h$-fragmentation of pattern $P$.
For any ball $\ball{}$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}$ for $P_{fi}$ via graph simulation,
and $M$ be the maximum match relation in $\ball{}$ for $P$ via graph simulation, respectively,
then $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
\end{theorem}

We also say that $M_i$ is a {\em partial match relation} in ball $\ball{}$ for $P$ via graph simulation.
%By Theorem~\ref{thm-compose}, instead of computing $M$ in $\ball{}$ \wrt\ $P$ directly, we can compute $M$ by first computing each $M_i$ in $\ball{}$ \wrt\ $P_{fi}$,
%and then combining them together.
By the nature of graph simulation~\cite{infsimu95}, $\bigcup_{i=1}^{h}M_{i}$ is actually an intermediate result of $M$.
%such that the method above does not incur additional computation cost.
Once we have the maximum match relation $M$ for $P$ in $\ball{}$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.

@@

%We already know that pattern updates $\Delta P$ on $P$ can be treated as the updates $\Delta P$ on $P_{fi}$ or $C$ of $P$.
%If we have cached the maximum match relations of all pattern fragments,
By storing $\tilde{M}(P,G)$, we have $\bigcup_{i=1}^{h}M_{i}$ for each ball $\ball{}$,
and we can simply update $M_i$ while leaving other parts untouched. That is, we indeed compute for $P_{fi}\oplus\Delta P(\ball{})$, instead of $P\oplus\Delta P(\ball{})$, and combine all $P_{fi}\oplus\Delta P(\ball{})$ to derive $P\oplus\Delta P(\ball{})$.
Even better, the updates $\Delta P$ on the cut $C$ of $P$ only involve with a simple combination process, avoiding the computation for any pattern fragments.

@@

\stitle{(II) Localization with affected balls (\affballsx)}.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computations.

@@

%\vspace{-0.5ex}
\stitle{(III) Algorithm framework}. We now provide a unified incremental algorithm to handle both pattern and data updates,
based on pattern fragmentation and affected balls.

@@

\etitle{(1) Identifying \affballsx}.
Algorithm \inc invokes two different procedures to identify \affballsx for separate $\Delta P$ or $\Delta G$, respectively.
For  simultaneous $\Delta P$ and $\Delta G$, \inc takes the union of the \affballsx produced by  the two procedures.

\etitle{(2) Update partial match relations in \affballsx}.
For a ball affected by $\Delta P$, \inc updates the partial match relations for the updated pattern fragments with incremental computation;
For a ball affected by $\Delta G$, \inc updates the partial match relations for all pattern fragments;
And, for a ball affected by both $\Delta P$ and $\Delta G$, \inc follows the same way as it does for $\Delta G$ only.
Meanwhile, auxiliary structure \fb (to be seen shortly) is updated for handling continuously separate and simultaneous pattern and data updates.

\etitle{(3) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
	\begin{center}
		\subfigure{\label{fig-auxstr-index}
			\includegraphics[scale=0.585]{./fig/fig-auxstr-index.eps}}
		\subfigure{\label{fig-inc-maintain-unit}
			\quad\quad \vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-unit.eps}}
		\subfigure{\label{fig-inc-maintain-batch}
			\vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-batch.eps}}
		\vspace{-2ex}
		\caption{Example auxiliary data structures}
		\label{fig-auxiliary-structures}
		\vspace{-5ex}
	\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-10-01 TF-vldb2018/sec-intro.tex

\stab (4) Using real-life data (\citationd) and synthetic data (\synthetic), we demonstrate the effectiveness and efficiency of our graph pattern matching approach for (dynamic) team formation (Section~\ref{sec-expt}).
We find that (a) our method is able to identify more sensible teams than existing team formation methods \wrt \eat{three} practical measurements,
and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 36\% for pattern updates, 34\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuous simultaneous pattern and data updates, respectively.

@@

Incremental algorithms (see \cite{inc-survey,FanHT17} for a survey) have proven usefulness in a variety of applications,
and have been studied for graph pattern matching~\cite{FanLMTWW10,FanWW13-tods} and team formation \cite{ArisLuca12} as well.
However, \cite{inc-survey,FanHT17,FanLMTWW10,FanWW13-tods} only consider data updates,
and \cite{ArisLuca12} only considers continuous coming new tasks. In this work, we  deal with both pattern and data updates for team formation, and support both insertions and deletions. To our knowledge, this is the first study on pattern updates, and is the most general and practical dynamic setting considered so far.

>>>>

\stab (4) Using real-life data (\citationd) and synthetic data (\synthetic), we demonstrate the effectiveness and efficiency of our graph pattern matching approach for (dynamic) team formation (Section~\ref{sec-expt}).
We find that (a) our method is able to identify more sensible teams than existing team formation methods \wrt \eat{three} practical measurements,
and (b) our incremental algorithm outperforms our batch algorithm, even when changes reach 36\% for pattern updates, 34\% for data updates and (25\%, 22\%) for simultaneous pattern and data updates, and when 29\% for continuous pattern updates, 26\% for continuous data updates and (20\%, 18\%) for continuously simultaneous pattern and data updates, respectively.

@@

Incremental algorithms (see \cite{inc-survey,FanHT17} for a survey) have proven usefulness in a variety of applications,
and have been studied for graph pattern matching~\cite{FanLMTWW10,FanWW13-tods} and team formation \cite{ArisLuca12} as well.
However, \cite{inc-survey,FanHT17,FanLMTWW10,FanWW13-tods} only consider data updates,
and \cite{ArisLuca12} only considers continuously coming new tasks. In this work, we  deal with both pattern and data updates for team formation, and support both insertions and deletions. To our knowledge, this is the first study on pattern updates, and is the most general and practical dynamic setting considered so far.
